---
title: "Cluster comparison"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    toc: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = F)
```

# Description

> Plots comparing clusters from questionnaire (immune groups) and hierarchical clustering. 

Using `r ifelse(low_conc_s, "low", "normal")` concentration S.

# Tables

```{r}
tar_load(seroclust_table)
seroclust_table
```

# Plots

```{r, fig.height=3, fig.width=9}
tar_load(seroclust_hm)
seroclust_hm$hcl
```

```{r, fig.height=3, fig.width=9}
seroclust_hm$qst
```

## Serocluster comparisons

```{r, fig.width=6, fig.height=4, warning=FALSE}
tar_load(seroclust_upset)
seroclust_upset
```

```{r, fig.height=7, fig.width=8}
tar_load(seroclust_boxplt)
seroclust_boxplt
```

```{r, fig.height=3, fig.width=12, warning=F}
tar_load(seroclust_response)
# seroclust_response$questionnaire
```

```{r, fig.height=3, fig.width=9, warning=F}
seroclust_response$hierarchical
```

## Protein-serocluster associations

Kruskal-Wallis p-values

```{r, fig.height=4, fig.width=4}
tar_load(prot_seroclust_plts)
tar_load(prot_seroclust_boxplts)
prot_seroclust_plts$qq_plots
```

Wilcoxon rank-sum test p-values, pairwise comparisons of serocluster protein levels

```{r, fig.height=7, fig.width=9}
prot_seroclust_plts$wilcox_hm
```

Boxplots are saved in a pdf file: **`r prot_seroclust_boxplts`**


## Mismatching samples

```{r}
tar_load(seroclust_mismatch)
```

```{r}
seroclust_mismatch$boxplots
```

```{r, fig.height=4, fig.width=10}
seroclust_mismatch$barplots
```


# Session information

```{r}
sessionInfo()
```